---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `unitModalReg`: A Collection of Parametric Modal Regressions Models for Bounded Data

<!-- badges: start -->
<!-- badges: end -->

The goal of `unitModalReg` is to provide tools for fitting parametric modal regression models
for bounded response variables.


## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("AndrMenezes/unitModalReg")
```

## Example

The packages follows the structure of `glm` objects. The main function is `unitModalReg`.

```{r example, warning=FALSE}
library(unitModalReg)

# Simulate data
n <- 500
betas <- c(beta0 = 2, beta1 = -1, beta2 = 0.6)
x1  <- runif(n)
x2  <- rbinom(n, size = 1, prob = 0.65)
eta <- betas[1] + betas[2] * x1 + betas[3] * x2
mu  <- exp(eta) / exp(1 + eta)
phi <- 4
y   <- rugamma(n = n, mu = mu, phi = phi)
data_sim <- data.frame(y = y, x1 = x1, x2 = factor(x2))

# Families of distributions
distr <- list(
  Be = "betaMode",
  UGz = "unitGompertz",
  UGa = "unitGamma",
  Kum = "Kumaraswamy"
)

# Fit the models
fits <- lapply(distr, function(m) {
  unitModalReg(y ~ x1 + x2, data = data_sim, family = m, link = "logit")
})

# Get the coefficients
vapply(fits, coef, numeric(4))
```

We also implemented the `gof` function to compare the models based on the information criterion (AIC, BIC and HQIC)
and [Voung test](https://en.wikipedia.org/wiki/Vuong's_closeness_test) for non-nested models.

```{r}
# Compare the models fitting
gof(lt = fits)
```


The currently methods implemented are
```{r methods}
methods(class = "unitModalReg")
```
